---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```

# invariance

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

The goal of `invariance` is to help users to perform the first step in Meucci's Checklist: __The Quest for Invariance__.



## Installation

You can install the development version of `invariance` with the following command:

``` r
# install.packages("devtools")
devtools::install_github("Reckziegel/CMA")
```

## Example


```{r example}
library(invariance)
library(tibble)

x <- as_tibble(diff(log(EuStockMarkets)))
x
```

The main statistics of a time-series can be summarized with `series_describe`:

```{r}
series_describe(x)
```

To check if an asset is stationary - "invariant"- use the `plot_ellipsoid` function:

```{r, out.height="80%", out.width="90%"}
# must be univariate
plot_ellipsoid(x[ , 1]) 
```

For "invariant" time-series, the shape of the ellipsoid present a circular format, like the example above.

To see if a distribution shows any evidence of changing behavior due to passage of time use `ks_test`:

```{r, out.height="80%", out.width="90%"}
ks_test(x[ , 1])
```

This is the famous non-parametric Kolmogorov-Smirnov test that tries to identify if two continuous series are draw from the same reference distribution.

## Reference

- Meucci, Attilio, ‘The Prayer’ Ten-Step Checklist for Advanced Risk and Portfolio Management (February 2, 2011). Available at SSRN: https://ssrn.com/abstract=1753788 or http://dx.doi.org/10.2139/ssrn.1753788
