---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```

# invariance

<!-- badges: start -->

[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental) [![R-CMD-check](https://github.com/Reckziegel/invariance/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/Reckziegel/invariance/actions/workflows/R-CMD-check.yaml)

<!-- badges: end -->

The goal of `invariance` is to help users to perform the first step in Meucci's Checklist: **The Quest for Invariance**.

## Installation

You can install the development version of `invariance` from Github with `devtools`:

``` r
# install.packages("devtools")
devtools::install_github("Reckziegel/invariance")
```

## Example

```{r example}
library(invariance)
library(tibble)

# Log-returns as candidates for invariance
x <- as_tibble(diff(log(EuStockMarkets)))
x
```

The main statistics of a time-series can be summarized with `series_describe`:

```{r}
series_describe(x)
```

To check if a series is stationary - "invariant" - use `invariance_test:`

```{r, out.height="80%", out.width="90%"}
# must be univariate
invariance_test(x["CAC"])
```

For "invariant" time-series the shape of the ellipsoid should be circular and the histograms should look the same.

To test if a distribution shows any evidence of changing behavior due to structural breaks, regime shifts, etc. use `ks_test`:

```{r, out.height="80%", out.width="90%"}
ks_test(x[ , 1])
```

If the two pieces of the distribution are statistically different a Bayesian estimation technique may be recommended in the next step of the Checklist: **Estimation**.

## Reference

-   Meucci, Attilio, ‘The Prayer’ Ten-Step Checklist for Advanced Risk and Portfolio Management (February 2, 2011). Available at SSRN: <https://ssrn.com/abstract=1753788> or <http://dx.doi.org/10.2139/ssrn.1753788>
